Beyond Static Retrieval: Adaptive Method for Improving RAG Performance

### 2025-04-15 Paper/TOSUBMIT/RAG_PAPER2.tex
Version to submit

\title[Article Title]{Beyond Static Retrieval: Adaptive Method for Improving RAG Performance}

@@

\abstract{Retrieval-Augmented Generation (RAG) enhances language model responses by incorporating external knowledge. However, its effectiveness heavily depends on the quality of the retrieved documents. Using a fixed number of retrieved documents K may fail  to adapt to varying query complexity, often leading to suboptimal retrieval either including irrelevant documents or missing crucial ones. To address this issue, we propose a hybrid method that dynamically adjusts K based on query characteristics while maintaining computational efficiency. Our method improves retrieval performance by maximizing relevant information and minimizing noise. Experimental results show that it outperforms fixed-K retrieval, offering a more effective solution for optimizing RAG systems. Compared to traditional methods, it dynamically adjusts based on the query and dataset characteristics, offering greater adaptability across various contexts.}

@@

Large Language Models (LLMs) have emerged as state-of-the-art artificial intelligence systems that excel at understanding and generating human-like text\cite{Radford2019}, Built on deep learning architectures, particularly transformers \cite{vaswani2017attention},these models showcase impressive adaptability across diverse tasks, such as machine translation\cite{Gu2018SearchEngine}, text generation\cite{liang2024controllabletextgenerationlarge} and question answering\cite{Zhang2023}. Notable examples of LLMs include OpenAI GPT series\cite{brown2020language}, Google BERT\cite{devlin2018bert} and T5 \cite{raffel2020exploring}. Despite their impressive capabilities, LLMs suffer from hallucination\cite{ji2023survey}, often generating confident but incorrect information. This is a critical challenge for knowledge-intensive tasks requiring high accuracy\cite{kandpal2023large}. Additionally, their static nature being trained on fixed datasets\cite{bender2021dangers} limits their ability to update knowledge dynamically, making them prone to outdated or inconsistent responses, especially for time-sensitive information.\cite{Mousavi2025}.

@@

In this paper, we investigate the problem of selecting K in RAG and propose a novel approach to dynamically adjust K based on  thresholds and a Mixture of Logits (MoL)\cite{ding2024efficient} scoring mechanism, ensuring efficient and context-sensitive candidate selection while reducing computational costs. The use of  adaptive thresholds algorithm improves the relevance of retrieved documents, refining the set to include only the most contextually appropriate matches. Unlike traditional approaches, it adapts to the query and dataset characteristics, making it more flexible for diverse contexts. Furthermore, its design for handling large datasets ensures scalable and precise retrieval, which is crucial for RAG systems working with extensive corpora.

@@

\section{Overview of Retrieval-Augmented Generation }\label{sec3}
Retrieval-Augmented Generation (RAG) is a method designed to enhance the performance of large language models (LLMs) by integrating external, reliable knowledge sources into their response generation process\cite{awsRAG}. RAG combines search capabilities with LLM prompting. The process involves feeding both the userss query and the relevant information retrieved by a search algorithm into the LLMs prompt\cite{ilin2023advancedrag}, enabling the model to generate answers based on the provided context.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.9\textwidth]{rag.JPG}
	\caption{RAG system component\cite{sharma2024rag}. }\label{rag.PNG}
\end{figure}
As illustrated in figure \ref{rag.PNG}, the RAG system is built around two main components: the retriever and the generator. The retriever's role is to find relevant information from a pre-built data store, while the generator utilizes this retrieved data to produce coherent and contextually appropriate content. The overall RAG process operates as follows :
\subsection{Retrieval in RAG Systems}\label{subsec2}

@@

where each key \( k_i \) is linked to a corresponding value \( v_i \) (often, the key and value are the same). When a query \( q \) is provided, the goal is to find the top-\( k \) keys that are most similar to the query using a similarity function \( s \), and then retrieve their associated values\cite{gupta2024comprehensivesurveyretrievalaugmentedgeneration}.

@@

\section{Proposed Solution}\label{sec3}
In traditional candidate selection systems, the reliance on static or fixed top-K retrieval lead to suboptimal retrieval performance, especially in scenarios where the relevance distribution of candidates is highly variable. In this section, we introduce the Mixture of Logits (MoL) and describe its role in representing a learned similarity function. Table \ref{tab:Notations_table} summarizes the notations used in this paper and we propose Dynamic Candidate Selection, a novel algorithm that adaptively refines the candidate selection process by leveraging component-level embeddings and a Mixture of Logits (MoL) scoring mechanism.

@@

	\item \textbf{Normalized Discounted Cumulative Gain (NDCG)}: Assesses the ranking quality while accounting for position importance. The NDCG@\( k \) is computed as:\cite{eviden2025mrr}
	\begin{equation}
		\text{NDCG@}k = \frac{1}{|U|} \sum_{u=1}^{|U|} \frac{\text{DCG@}k}{\text{IDCG@}k},
	\end{equation}
	where \( \text{DCG@}k \) is the Discounted Cumulative Gain at position \( k \):
	\begin{equation}
		\text{DCG@}k = \sum_{i=1}^{k} \frac{2^{\text{rel}_i} - 1}{\log_2(i + 1)},
	\end{equation}
	and \( \text{IDCG@}k \) is the Ideal DCG@\( k \), computed by sorting the items by their true relevance scores.
\end{itemize}  
\section{Experimental Results}\label{sec3}
In order to measure the effectiveness of our proposed method, we perform a comprehensive evaluation of both the retrieval algorithm and the Mixture-of-Logits (MoL) approach. This assessment focuses on the next-item prediction task, a fundamental challenge in recommendation systems\cite{Zhu_2018}\cite{kang2018selfattentivesequentialrecommendation}, where the goal is to predict the most relevant item a user will interact with next based on their past interactions. 
\subsection{Dataset}
We conducted experiments using two MovieLens datasets : ML-100K and ML-1M \cite{Harper2015}which are widely used benchmarks for evaluating sequential recommendation models as detailed in Table\ref{tab:movielens}.\\
\begin{table}[h]
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{tabular}{|l|p{10cm}|}
		\hline
		\textbf{Dataset} & \textbf{Description} \\
		\hline
		\textbf{MovieLens-100K} & 100,000 ratings (1-5 scale) from 943 users on 1,682 movies. \\
		& Each user has rated at least 20 movies. \\
		& Includes user demographic information (age, gender, occupation, zip code). \\
		\hline
		\textbf{MovieLens-1M} & 1,000,209 ratings from 6,040 users on approximately 3,900 movies. \\
		& Data collected from users who joined MovieLens in 2000. \\
		& Represents a larger-scale recommendation scenario. \\
		\hline
	\end{tabular}
	\caption{Summary of MovieLens datasets}
	\label{tab:movielens}
\end{table}

\subsection{ Setup }
For both datasets, We utilize the SASRec architecture as our sequential user encoder, a model renowned for achieving state-of-the-art performance in next-item prediction tasks. This architecture processes the user's historical interaction sequence, generating embeddings that encapsulate the user's preferences at each time step. These embeddings serve as the foundation for predicting the next item in the sequence.

@@

\begin{table}[ht]
	\centering
	\large
	\renewcommand{\arraystretch}{1.7} % Increase row spacing
	\resizebox{\textwidth}{!}{  % Scale table to fit width
		\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
		      \hline
		 \textbf{Model} & \textbf{\shortstack{Max \\ Sequence Length}} & 
		 \textbf{\shortstack{Embedding \\ Dimension}} & 
		 \textbf{\shortstack{Number \\ of Heads}} & 
		 \textbf{\shortstack{Feedforward \\ Dimension}} & 
		 \textbf{\shortstack{Batch \\ Size}} & 
		 \textbf{Epochs} & 
		 \textbf{\shortstack{Val \\ Loss}} & 
		 \textbf{\shortstack{Val \\ Accuracy}} \\
		 \hline
			Hybrid+SAS & 50  & 128  & 2 & 128  & 128 & 12 & 5.3036 & 0.1584  \\ \hline
			MoL+SAS    & 50  & 128  & 2 & 128  & 128 & 12 & 5.3152 & 0.1582  \\ \hline
			Hybrid+SAS & 128 & 256  & 4 & 256  & 128 & 10 & 3.6364 & 0.4301  \\ \hline
			MoL+SAS    & 128 & 256  & 4 & 256  & 128 & 10 & 3.6374 & 0.4299 \\\hline
			Hybrid+SAS & 512 & 512  & 4 & 512  & 128 & 10 & 1.2808 & 0.8120 \\ \hline
			MoL+SAS    & 512 & 512  & 4 & 512  & 128 & 10 & 1.3050 & 0.8016 \\\hline
   \end{tabular}
}
\caption{Results on 100kMovies dataset}
\label{tab:100k_movies}
\end{table}

@@

\begin{table}[ht]
	\centering
	\large
	\renewcommand{\arraystretch}{1.7} % Increase row spacing
	\resizebox{\textwidth}{!}{  % Scale table to fit width
		\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
		    \hline
		\textbf{Model} & \textbf{\shortstack{Max \\ Sequence Length}} & 
		\textbf{\shortstack{Embedding \\ Dimension}} & 
		\textbf{\shortstack{Number \\ of Heads}} & 
		\textbf{\shortstack{Feedforward \\ Dimension}} & 
		\textbf{\shortstack{Batch \\ Size}} & 
		\textbf{Epochs} & 
		\textbf{\shortstack{Val \\ Loss}} & 
		\textbf{\shortstack{Val \\ Accuracy}} \\
		\hline
			Hybrid+SAS & 50  & 128  & 2 & 128  & 128 & 10 & 4.5721 & 0.1530  \\ \hline
			MoL+SAS    & 50  & 128  & 2 & 128  & 128 & 10 & 4.5733 & 0.1526  \\ \hline
			Hybrid+SAS & 128 & 256  & 4 & 256  & 128 & 10 & 3.4152 & 0.3680  \\ \hline
			MoL+SAS    & 128 & 256  & 4 & 256  & 128 & 10 & 3.4671 & 0.3627  \\ \hline
			Hybrid+SAS & 512 & 512  & 4 & 512  & 128 & 10 & 1.0275 & 0.8350  \\ \hline
			MoL+SAS    & 512 & 512  & 4 & 512  & 128 & 10 & 1.0350 & 0.8276  \\ \hline

@@

Choosing the right value for K in retrieval-based systems is a significant challenge, as it directly impacts both the efficiency and accuracy of information retrieval. While using a fixed K is straightforward, it often fails to adapt to the varying complexities of different queries. This can result in either missing important information or retrieving irrelevant data, which adds noise to the results. On the other hand, dynamically adjusting K offers greater flexibility but comes with its own set of challenges, such as increased computational costs and inconsistencies in determining the optimal retrieval size.
To address these limitations, we introduced a hybrid dynamic K selection strategy that strikes a balance between adaptability and efficiency. Our approach adjusts K based on the unique characteristics of each query while keeping computational demands manageable. This method has shown promising results, improving retrieval performance by minimizing unnecessary noise and ensuring that critical information is consistently captured.
Future work can explore enhancing our model with learning-based retrieval strategie such as reinforcement learning or attention mechanisms could refine the dynamic selection of K Additionally, testing our approach in real-world scenarios and conducting large-scale evaluations across diverse domains will help validate its robustness and adaptability in various knowledge bases and retrieval settings.

>>>>

	\title[Article Title]{dyRAG: Dynamic Retrieval Augmentation for Adaptive RAG Performance}

@@

	\abstract{Retrieval-Augmented Generation (RAG) enhances language model responses by incorporating external knowledge. However, its effectiveness heavily depends on the quality of the retrieved documents. Using a fixed number of retrieved documents K may fail  to adapt to varying query complexity, often leading to suboptimal retrieval either including irrelevant documents or missing crucial ones. To address this issue, we propose dyRAG, a hybrid method that dynamically adjusts K based on query characteristics while maintaining computational efficiency. Our method improves retrieval performance by maximizing relevant information and minimizing noise. Experimental results show that it outperforms fixed-K retrieval, offering a more effective solution for optimizing RAG systems. Compared to traditional methods, it dynamically adjusts based on the query and dataset characteristics, offering greater adaptability across various contexts.}

@@

	Large Language Models (LLMs) have emerged as state-of-the-art artificial intelligence systems that excel at understanding and generating human-like text\cite{Radford2019}, Built on deep learning architectures, particularly transformers \cite{vaswani2017attention},these models showcase impressive adaptability across diverse tasks, such as machine translation\cite{Gu2018SearchEngine}, text generation\cite{liang2024controllabletextgenerationlarge} and question answering\cite{Zhang2023}. Notable examples of LLMs include OpenAI GPT series\cite{brown2020language}, Google BERT\cite{devlin2018bert} and T5 \cite{raffel2020exploring}. Despite their impressive capabilities, LLMs suffer from hallucination\cite{Radford2019}, often generating confident but incorrect information. This is a critical challenge for knowledge-intensive tasks requiring high accuracy\cite{Radford2019}. Additionally, their static nature being trained on fixed datasets\cite{Radford2019} limits their ability to update knowledge dynamically, making them prone to outdated or inconsistent responses, especially for time-sensitive information.\cite{Mousavi2025}.

@@

	In this paper, we investigate the problem of selecting K in RAG and propose a novel approach to dynamically adjust K based on  thresholds and a Mixture of Logits (MoL)\cite{ding2024efficient} scoring mechanism, ensuring efficient and context-sensitive candidate selection while reducing computational costs. The use of  adaptive thresholds algorithm improves the relevance of retrieved documents, refining the set to include only the most contextually appropriate matches. Unlike traditional approaches, dyRAG adapts to the query and dataset characteristics, making it more flexible for diverse contexts. Furthermore, its design for handling large datasets ensures scalable and precise retrieval, which is crucial for RAG systems working with extensive corpora.

@@

	\section{Overview of Retrieval-Augmented Generation }\label{sec3}
	Retrieval-Augmented Generation (RAG) is a method designed to enhance the performance of large language models (LLMs) by integrating external, reliable knowledge sources into their response generation process\cite{awsRAG}. RAG combines search capabilities with LLM prompting. The process involves feeding both the userss query and the relevant information retrieved by a search algorithm into the LLMs prompt\cite{ilin2023advancedrag}, enabling the model to generate answers based on the provided context.
	gupta20241
	\begin{figure}[h]
		\centering
		\includegraphics[width=0.9\textwidth]{rag.JPG}
		\caption{RAG system component\cite{gupta20241}. }\label{rag.PNG}
	\end{figure}
	As illustrated in figure \ref{rag.PNG}, the RAG system is built around two main components: the retriever and the generator. The retriever's role is to find relevant information from a pre-built data store, while the generator utilizes this retrieved data to produce coherent and contextually appropriate content. The overall RAG process operates as follows :
	\subsection{Retrieval in RAG Systems}\label{subsec2}

@@

	where each key \( k_i \) is linked to a corresponding value \( v_i \) (often, the key and value are the same). When a query \( q \) is provided, the goal is to find the top-\( k \) keys that are most similar to the query using a similarity function \( s \), and then retrieve their associated values\cite{gupta20241}.

@@

	\section{dyRAG: The proposed Solution}\label{sec3}
	In traditional candidate selection systems, the reliance on static or fixed top-K retrieval lead to suboptimal retrieval performance, especially in scenarios where the relevance distribution of candidates is highly variable. In this section, we introduce the Mixture of Logits (MoL) and describe its role in representing a learned similarity function. Table \ref{tab:Notations_table} summarizes the notations used in this paper and we propose Dynamic Candidate Selection, a novel algorithm that adaptively refines the candidate selection process by leveraging component-level embeddings and a Mixture of Logits (MoL) scoring mechanism.

@@

		\item \textbf{Normalized Discounted Cumulative Gain (NDCG)}: Assesses the ranking quality while accounting for position importance. The NDCG@\( k \) is computed as:\cite{eviden2025mrr}
		\begin{equation}
		\text{NDCG@}k = \frac{1}{|U|} \sum_{u=1}^{|U|} \frac{\text{DCG@}k}{\text{IDCG@}k},
		\end{equation}
		where \( \text{DCG@}k \) is the Discounted Cumulative Gain at position \( k \):
		\begin{equation}
		\text{DCG@}k = \sum_{i=1}^{k} \frac{2^{\text{rel}_i} - 1}{\log_2(i + 1)},
		\end{equation}
		and \( \text{IDCG@}k \) is the Ideal DCG@\( k \), computed by sorting the items by their true relevance scores.
	\end{itemize}  
	\section{Experimental Results}\label{sec3}
	In order to measure the effectiveness of our proposed method, we perform a comprehensive evaluation of both the retrieval algorithm and the Mixture-of-Logits (MoL) approach. This assessment focuses on the next-item prediction task, a fundamental challenge in recommendation systems\cite{Zhu_2018}\cite{kang2018selfattentivesequentialrecommendation}, where the goal is to predict the most relevant item a user will interact with next based on their past interactions. 
	\subsection{Dataset description}
	We conducted experiments using two MovieLens datasets : ML-100K and ML-1M \cite{Harper2015}which are widely used benchmarks for evaluating sequential recommendation models as detailed in Table\ref{tab:movielens}.\\
	\begin{table}[h]
		\centering
		\renewcommand{\arraystretch}{1.2}
		\begin{tabular}{|l|p{10cm}|}
			\hline
			\textbf{Dataset} & \textbf{Description} \\
			\hline
			\textbf{MovieLens-100K} & 100,000 ratings (1-5 scale) from 943 users on 1,682 movies. \\
			& Each user has rated at least 20 movies. \\
			& Includes user demographic information (age, gender, occupation, zip code). \\
			\hline
			\textbf{MovieLens-1M} & 1,000,209 ratings from 6,040 users on approximately 3,900 movies. \\
			& Data collected from users who joined MovieLens in 2000. \\
			& Represents a larger-scale recommendation scenario. \\
			\hline
		\end{tabular}
		\caption{Summary of MovieLens datasets}
		\label{tab:movielens}
	\end{table}
	\subsection{ Experiments Setup }
	For both datasets, We utilize the SASRec architecture as our sequential user encoder, a model renowned for achieving state-of-the-art performance in next-item prediction tasks. This architecture processes the user's historical interaction sequence, generating embeddings that encapsulate the user's preferences at each time step. These embeddings serve as the foundation for predicting the next item in the sequence.

@@

	\begin{table}[ht]
		\centering
		\large
		\renewcommand{\arraystretch}{1.7} % Increase row spacing
		\resizebox{\textwidth}{!}{  % Scale table to fit width
			\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
				\hline
				\textbf{Model} & \textbf{\shortstack{Max \\ Sequence Length}} & 
				\textbf{\shortstack{Embedding \\ Dimension}} & 
				\textbf{\shortstack{Number \\ of Heads}} & 
				\textbf{\shortstack{Feedforward \\ Dimension}} & 
				\textbf{\shortstack{Batch \\ Size}} & 
				\textbf{Epochs} & 
				\textbf{\shortstack{Val \\ Loss}} & 
				\textbf{\shortstack{Val \\ Accuracy}} \\
				\hline
				Hybrid+SAS & 50  & 128  & 2 & 128  & 128 & 12 & 5.3036 & 0.1584  \\ \hline
				MoL+SAS    & 50  & 128  & 2 & 128  & 128 & 12 & 5.3152 & 0.1582  \\ \hline
				Hybrid+SAS & 128 & 256  & 4 & 256  & 128 & 10 & 3.6364 & 0.4301  \\ \hline
				MoL+SAS    & 128 & 256  & 4 & 256  & 128 & 10 & 3.6374 & 0.4299 \\\hline
				Hybrid+SAS & 512 & 512  & 4 & 512  & 128 & 10 & 1.2808 & {\bf 0.8120} \\ \hline
				MoL+SAS    & 512 & 512  & 4 & 512  & 128 & 10 & 1.3050 & 0.8016 \\\hline
			\end{tabular}
		}
		\caption{Results on 100kMovies dataset}
		\label{tab:100k_movies}
	\end{table}

@@

	\begin{table}[ht]
		\centering
		\large
		\renewcommand{\arraystretch}{1.7} % Increase row spacing
		\resizebox{\textwidth}{!}{  % Scale table to fit width
			\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
				\hline
				\textbf{Model} & \textbf{\shortstack{Max \\ Sequence Length}} & 
				\textbf{\shortstack{Embedding \\ Dimension}} & 
				\textbf{\shortstack{Number \\ of Heads}} & 
				\textbf{\shortstack{Feedforward \\ Dimension}} & 
				\textbf{\shortstack{Batch \\ Size}} & 
				\textbf{Epochs} & 
				\textbf{\shortstack{Val \\ Loss}} & 
				\textbf{\shortstack{Val \\ Accuracy}} \\
				\hline
				Hybrid+SAS & 50  & 128  & 2 & 128  & 128 & 10 & 4.5721 & 0.1530  \\ \hline
				MoL+SAS    & 50  & 128  & 2 & 128  & 128 & 10 & 4.5733 & 0.1526  \\ \hline
				Hybrid+SAS & 128 & 256  & 4 & 256  & 128 & 10 & 3.4152 & 0.3680  \\ \hline
				MoL+SAS    & 128 & 256  & 4 & 256  & 128 & 10 & 3.4671 & 0.3627  \\ \hline
				Hybrid+SAS & 512 & 512  & 4 & 512  & 128 & 10 & 1.0275 & {\bf 0.8350} \\ \hline
				MoL+SAS    & 512 & 512  & 4 & 512  & 128 & 10 & 1.0350 & 0.8276  \\ \hline

@@

	Choosing the right value for K in retrieval-based systems is a significant challenge, as it directly impacts both the efficiency and accuracy of information retrieval. While using a fixed K is straightforward, it often fails to adapt to the varying complexities of different queries. This can result in either missing important information or retrieving irrelevant data, which adds noise to the results. On the other hand, dynamically adjusting K offers greater flexibility but comes with its own set of challenges, such as increased computational costs and inconsistencies in determining the optimal retrieval size.

	To address these limitations, we introduced a hybrid dynamic K selection strategy that strikes a balance between adaptability and efficiency. Our approach adjusts K based on the unique characteristics of each query while keeping computational demands manageable. This method has shown promising results, improving retrieval performance by minimizing unnecessary noise and ensuring that critical information is consistently captured.

	Future work can explore enhancing our model with learning-based retrieval strategies such as reinforcement learning or attention mechanisms could refine the dynamic selection of K Additionally, testing our approach in real-world scenarios and conducting large-scale evaluations across diverse domains will help validate its robustness and adaptability in various knowledge bases and retrieval settings.

### 2025-04-15 Paper/latex/paper_RAG.tex
Version to submit

Choosing the right value for K in retrieval-based systems is a significant challenge, as it directly impacts both the efficiency and accuracy of information retrieval. While using a fixed K is straightforward, it often fails to adapt to the varying complexities of different queries. This can result in either missing important information or retrieving irrelevant data, which adds noise to the results. On the other hand, dynamically adjusting K offers greater flexibility but comes with its own set of challenges, such as increased computational costs and inconsistencies in determining the optimal retrieval size.
To address these limitations, we introduced a hybrid dynamic K selection strategy that strikes a balance between adaptability and efficiency. Our approach adjusts K based on the unique characteristics of each query while keeping computational demands manageable. This method has shown promising results, improving retrieval performance by minimizing unnecessary noise and ensuring that critical information is consistently captured.
Future work can explore enhancing our model with learning-based retrieval strategie such as reinforcement learning or attention mechanisms could refine the dynamic selection of K Additionally, testing our approach in real-world scenarios and conducting large-scale evaluations across diverse domains will help validate its robustness and adaptability in various knowledge bases and retrieval settings.

>>>>

Choosing the right value for K in retrieval-based systems is a significant challenge, as it directly impacts both the efficiency and accuracy of information retrieval. While using a fixed K is straightforward, it often fails to adapt to the varying complexities of different queries. This can result in either missing important information or retrieving irrelevant data, which adds noise to the results. On the other hand, dynamically adjusting K offers greater flexibility but comes with its own set of challenges, such as increased computational costs and inconsistencies in determining the optimal retrieval size.
To address these limitations, we introduced a hybrid dynamic K selection strategy that strikes a balance between adaptability and efficiency. Our approach adjusts K based on the unique characteristics of each query while keeping computational demands manageable. This method has shown promising results, improving retrieval performance by minimizing unnecessary noise and ensuring that critical information is consistently captured.
Future work can explore enhancing our model with learning-based retrieval strategies such as reinforcement learning or attention mechanisms could refine the dynamic selection of K Additionally, testing our approach in real-world scenarios and conducting large-scale evaluations across diverse domains will help validate its robustness and adaptability in various knowledge bases and retrieval settings.
